A Comparison of Algorithms Playing EvoMan

### 2020-07-20 paper/paper.tex
Updated report with results of specialized PPO against difficulty 5.
Ready for report.

    \subsection{Best Combination of Opponents for Training}\label{subsec:best-combination-of-opponents-for-training}
    We searched for the opponents that lead to the best results.
    The first combination of train opponents we considered was \{1, 2, 6, 7\} which was chosen empirically after manually playing against every opponent and chosing the ones which behaved in such a way that covered the most general concepts our agents could learn in our opinion.
    We observed its final gain as 125.37.
    We realized a set of exploratory experiments where we would search for other combinations of train opponents,
    but starting with the resulting model of PPO trained for 1000 epochs on the combination of opponents \{1, 2, 6, 7\}.
    If by starting with a pre-trained model another combination of train enemies does not lead to better results,
    then we can believe that the respective combination does not lead to better results than \{1, 2, 6, 7\}.
    \begin{table}[htbp]
        \caption{Results for various opponents when starting with a pre-trained PPO model on enemies \{1, 2, 6, 7\}}
        \begin{center}
            \begin{tabular}{|c|c|}
                \hline
                \textbf{Train opponents}&{\textbf{gain (harmonic mean)}} \\
                \hline
                $\{1, 2, 6, 7\} \cup \{3, 4, 5, 8\}$ & $44.16$ \\
                $\{1, 2, 6, 7\} \cup \{3, 4, 6, 7\}$ & $75.3$ \\
                $\{1, 2, 6, 7\} \cup \{1, 3, 6, 7\}$ & $110.19$ \\
                $\{1, 2, 6, 7\} \cup \{2, 3, 6, 7\}$ & $136.1$ \\
                $\{1, 2, 6, 7\} \cup \{2, 4, 6, 7\}$ & $85.22$ \\
                \hline
            \end{tabular}
            \label{table:variations_of_opponents}
        \end{center}
    \end{table}
    \\
    The only combination that lead to a better score than 125.37 was \{2, 3, 6, 7\}.
    We ran an experiment with PPO with random initialization with the combination of train enemies \{2, 3, 6, 7\} and
    we obtained a final gain of 99.97.
    This means that we did not find a better combination of train opponents than \{1, 2, 6, 7\}, so it is the one
    we used for the following experiments.

@@

    \begin{table}[htbp]
        \caption{Specialized NEAT vs Generalized PPO (Gain)}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|c|}
                \hline
                \textbf{Opponent}&\multicolumn{4}{|c|}{\textbf{PPO}}&\textbf{Specialized} \\
                \cline{2-5}
                & \textbf{\textit{Run 1}}& \textbf{\textit{Run 2}}& \multicolumn{2}{|c|}{\textbf{\textit{Run 3}}} & NEAT \\
                \cline{4-5}
                & 3000 ep & 3000 ep & 3000 ep & 1750 ep & \\
                & (best at training) & & & (best tested) & \\
                \hline
                1 & 198.41 & 199.07 & 199.81 & 199.61 & 190.01 \\
                2 & 199.74 & 199.27 & 190.34 & 189.14 & 194.01 \\
                3 & 58.94 & 46.67 & 70.27 & 85.01 & 180.01 \\
                4 & 58.34 & 66.5 & 64.11 & 80.17 & 194.01 \\
                5 & 172.61 & 165.65 & 174.61 & 158.83 & 194.01\\
                6 & 195.73 & 196.95 & 195.85 & 194.37 & 173.01 \\
                7 & 199.79 & 195.05 & 193.27 & 191.17 & 177.01 \\
                8 & 122.17 & 145.49 & 141.89 & 140.61 & 186.01 \\
                \hline
                \textbf{\{1, 2, 6, 7\}} & & & & & \\
                \textbf{harmonic mean} & 198.4 & 197.57 & 194.75 & 193.49 & 183.09 \\
                \hline
                \textbf{final} & & & & & \\
                \textbf{harmonic mean} & 117.22 & 114.91 & 127.01 & 137.18 & 185.67\\
                \hline

@@

    \begin{table}[htbp]
        \caption{Specialized NEAT vs Generalized PPO (Percentage of games won)}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|}
                \hline
                \textbf{Opponent}&\multicolumn{4}{|c|}{\textbf{PPO}} \\
                \cline{2-5}
                & \textbf{\textit{Run 1}}& \textbf{\textit{Run 2}}& \multicolumn{2}{|c|}{\textbf{\textit{Run 3}}} \\
                \cline{4-5}
                & 3000 ep & 3000 ep & 3000 ep & 1750 ep\\
                & (best at training) & & & (best tested) \\
                \hline
                1 & 100 & 100 & 100 & 100 \\
                2 & 100 & 100 & 100 & 100 \\
                3 & 3.33 & 0 & 3.33 & 46.66 \\
                4 & 0 & 6.66 & 0 & 6.66 \\
                5 & 100 & 96.66 & 100 & 100 \\
                6 & 100 & 100 & 100 & 100 \\
                7 & 100 & 93.33 & 100 & 100 \\
                8 & 80 & 100 & 96.66 & 90 \\
                \hline

@@

    \begin{table}[htbp]
        \caption{Average player and enemy life. Average game duration}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|c|c|}
                \hline
                \textbf{Opponent}&\multicolumn{3}{|c|}{\textbf{Best train agent}}&\multicolumn{3}{|c|}{\textbf{Best test agent}} \\
                \cline{2-7}
                & \textbf{\textit{Avg player life}}& \textbf{\textit{Avg enemy life}}& \textbf{\textit{Avg duration}} & \textbf{\textit{Avg player life}}& \textbf{\textit{Avg enemy life}}& \textbf{\textit{Avg duration}} \\
                \hline
                1 & 97.26 &     0 &  159.63 &    100 &     0 &  174.23 \\
                2 & 98.33 &     0 &   176.6 &  89.73 &     0 &  186.43 \\
                3 &  0.13 & 43.33 &  457.26 &   7.66 & 21.33 &  410.53 \\
                4 &     0 & 37.66 &   547.5 &   1.84 & 21.66 &  736.83 \\
                5 & 71.32 &     0 &  379.13 &  60.52 &     0 &  367.93 \\
                6 & 96.32 &     0 &  165.06 &     95 &     0 &  203.53 \\
                7 & 99.74 &     0 &  162.06 &   85.9 &     0 &  135.13 \\
                8 &  34.3 &     6 &  520.93 &  38.76 &     2 &   443.6 \\
                \hline
                \textbf{Average} & 62.17 & 10.87 & 321.02 & 59.92 & 5.62 & 332.27 \\
            \end{tabular}
        \end{center}
    \end{table}

@@

    \begin{table}[htbp]
        \caption{PPO trained against all opponents (Gain)}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|c|}
                \hline
                \textbf{Opponent}&\multicolumn{5}{|c|}{\textbf{Difficulty}} \\
                \cline{2-6}
                & \textbf{\textit{1}}& \textbf{\textit{2}}& \textbf{\textit{3}} & \textbf{\textit{4}} & \textbf{\textit{5}} \\
                \hline
                 1 &  200.01 &  199.54 &  170.75 &  155.48 &   41.08\\
                 2 &  200.01 &  200.01 &  182.81 &  168.81 &  168.51\\
                 3 &  199.38 &  194.81 &  164.31 &  127.54 &  130.61\\
                 4 &  186.14 &  180.61 &  154.23 &  181.58 &   60.28\\
                 5 &  196.56 &  187.77 &  185.34 &  142.41 &  158.31\\
                 6 &  196.35 &  174.43 &  179.19 &   23.84 &    9.88\\
                 7 &  199.26 &  183.07 &   95.40 &    8.01 &    8.28\\
                 8 &  196.57 &  169.31 &  123.00 &   41.34 &   10.01\\
                \hline
                \textbf{harmonic mean} & 196.68 & 185.57 & 149.57 & 35.76 & 20.89 \\
                \hline
            \end{tabular}
            \label{PPO against all opponents gain}
        \end{center}
    \end{table}

    \begin{table}[htbp]
        \caption{PPO trained against all opponents (percent games lost)}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|c|}
                \hline
                \textbf{Opponent}&\multicolumn{5}{|c|}{\textbf{Difficulty}} \\
                \cline{2-6}
                & \textbf{\textit{1}}& \textbf{\textit{2}}& \textbf{\textit{3}} & \textbf{\textit{4}} & \textbf{\textit{5}} \\
                \hline
                 1 &  0 &  0 &     20 &  23.33 &   100 \\
                 2 &  0 &  0 &      0 &      0 &     0 \\
                 3 &  0 &  0 &      0 &  13.33 &  3.33 \\
                 4 &  0 &  0 &      0 &      0 &    60 \\
                 5 &  0 &  0 &      0 &      0 &     0 \\
                 6 &  0 &  0 &      0 &    100 &   100 \\
                 7 &  0 &  0 &  56.66 &    100 &   100 \\
                 8 &  0 &  0 &     10 &    100 &   100 \\
                \hline
            \end{tabular}
            \label{PPO against all opponents games lost}
        \end{center}
    \end{table}

    \subsubsection{A PPO agent for each opponent}
    In the second attempt to outscore the upper bound we have trained an agent
    for each of the $8$ opponents.
    Due to the high computational time this experiment was done only at
    difficulty 2 and the number of training epochs for PPO was decreased from 3000 to 1000.
    It won all its games against all opponents at difficulty 2.
    \begin{table}[htbp]
        \caption{PPO generalized vs PPO specialized vs NEAT specialized}
        \begin{center}
            \begin{tabular}{|c|c|c|c|}
                \hline
                \textbf{Opponent}&\textbf{PPO g.}&\textbf{PPO s.}&\textbf{NEAT s.} \\
                \hline
                 1 &  199.54 &  199.67 &  190.01 \\
                 2 &  200.01 &  199.61 &  194.01 \\
                 3 &  194.81 &  199.94 &  180.01 \\
                 4 &  180.61 &  195.95 &  194.01 \\
                 5 &  187.77 &  198.03 &  194.01 \\
                 6 &  174.43 &  199.67 &  173.01 \\
                 7 &  183.07 &  197.73 &  177.01 \\
                 8 &  169.31 &  195.07 &  186.01 \\
                \hline
                \textbf{harmonic mean} & 185.57 & 198.19 & 185.67 \\
                \hline
            \end{tabular}
            \label{PPO generalized vs specialized vs NEAT}
        \end{center}
    \end{table}

@@

>>>>

    \subsection{Best Combination of Opponents for Training}\label{subsec:best-combination-of-opponents-for-training}
    We searched for the opponents that lead to the best results.
    The first combination of train opponents we considered was \{1, 2, 6, 7\} which was chosen empirically after manually playing against every opponent and chosing the ones which behaved in such a way that covered the most general concepts our agents could learn in our opinion.
    We observed its final gain as 125.37.
    We realized a set of exploratory experiments where we would search for other combinations of train opponents,
    but starting with the resulting model of PPO trained for 1000 epochs on the combination of opponents \{1, 2, 6, 7\}.
    If by starting with a pre-trained model another combination of train enemies does not lead to better results,
    then we can believe that the respective combination does not lead to better results than \{1, 2, 6, 7\}.
    \begin{table}[htbp]
        \caption{Results for various opponents when starting with a pre-trained PPO model on enemies \{1, 2, 6, 7\}}
        \begin{center}
            \begin{tabular}{|c|c|}
                \hline
                \textbf{Train opponents}             & {\textbf{gain (harmonic mean)}} \\
                \hline
                $\{1, 2, 6, 7\} \cup \{3, 4, 5, 8\}$ & $44.16$                         \\
                $\{1, 2, 6, 7\} \cup \{3, 4, 6, 7\}$ & $75.3$                          \\
                $\{1, 2, 6, 7\} \cup \{1, 3, 6, 7\}$ & $110.19$                        \\
                $\{1, 2, 6, 7\} \cup \{2, 3, 6, 7\}$ & $136.1$                         \\
                $\{1, 2, 6, 7\} \cup \{2, 4, 6, 7\}$ & $85.22$                         \\
                \hline
            \end{tabular}
            \label{table:variations_of_opponents}
        \end{center}
    \end{table}
    \\
    The only combination that lead to a better score than 125.37 was \{2, 3, 6, 7\}.
    We ran an experiment with PPO with random initialization with the combination of train enemies \{2, 3, 6, 7\} and
    we obtained a final gain of 99.97.
    This means that we did not find a better combination of train opponents than \{1, 2, 6, 7\}, so it is the one
    we used for the following experiments.

@@

    \begin{table}[htbp]
        \caption{Specialized NEAT vs Generalized PPO (Gain)}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|c|}
                \hline
                \textbf{Opponent} & \multicolumn{4}{|c|}{\textbf{PPO}} & \textbf{Specialized} \\
                \cline{2-5}
                & \textbf{\textit{Run 1}} & \textbf{\textit{Run 2}} & \multicolumn{2}{|c|}{\textbf{\textit{Run 3}}} & NEAT \\
                \cline{4-5}
                & 3000 ep            & 3000 ep & 3000 ep & 1750 ep       &        \\
                & (best at training) &         &         & (best tested) &        \\
                \hline
                1                       & 198.41             & 199.07  & 199.81  & 199.61        & 190.01 \\
                2                       & 199.74             & 199.27  & 190.34  & 189.14        & 194.01 \\
                3                       & 58.94              & 46.67   & 70.27   & 85.01         & 180.01 \\
                4                       & 58.34              & 66.5    & 64.11   & 80.17         & 194.01 \\
                5                       & 172.61             & 165.65  & 174.61  & 158.83        & 194.01 \\
                6                       & 195.73             & 196.95  & 195.85  & 194.37        & 173.01 \\
                7                       & 199.79             & 195.05  & 193.27  & 191.17        & 177.01 \\
                8                       & 122.17             & 145.49  & 141.89  & 140.61        & 186.01 \\
                \hline
                \textbf{\{1, 2, 6, 7\}} &                    &         &         &               &        \\
                \textbf{harmonic mean}  & 198.4              & 197.57  & 194.75  & 193.49        & 183.09 \\
                \hline
                \textbf{final}          &                    &         &         &               &        \\
                \textbf{harmonic mean}  & 117.22             & 114.91  & 127.01  & 137.18        & 185.67 \\
                \hline

@@

    \begin{table}[htbp]
        \caption{Specialized NEAT vs Generalized PPO (Percentage of games won)}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|}
                \hline
                \textbf{Opponent} & \multicolumn{4}{|c|}{\textbf{PPO}} \\
                \cline{2-5}
                & \textbf{\textit{Run 1}} & \textbf{\textit{Run 2}} & \multicolumn{2}{|c|}{\textbf{\textit{Run 3}}} \\
                \cline{4-5}
                & 3000 ep            & 3000 ep & 3000 ep & 1750 ep       \\
                & (best at training) &         &         & (best tested) \\
                \hline
                1 & 100                & 100     & 100     & 100           \\
                2 & 100                & 100     & 100     & 100           \\
                3 & 3.33               & 0       & 3.33    & 46.66         \\
                4 & 0                  & 6.66    & 0       & 6.66          \\
                5 & 100                & 96.66   & 100     & 100           \\
                6 & 100                & 100     & 100     & 100           \\
                7 & 100                & 93.33   & 100     & 100           \\
                8 & 80                 & 100     & 96.66   & 90            \\
                \hline

@@

    \begin{table}[htbp]
        \caption{Average player and enemy life. Average game duration}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|c|c|}
                \hline
                \textbf{Opponent} & \multicolumn{3}{|c|}{\textbf{Best train agent}} & \multicolumn{3}{|c|}{\textbf{Best test agent}} \\
                \cline{2-7}
                & \textbf{\textit{Avg player life}} & \textbf{\textit{Avg enemy life}} & \textbf{\textit{Avg duration}} & \textbf{\textit{Avg player life}} & \textbf{\textit{Avg enemy life}} & \textbf{\textit{Avg duration}} \\
                \hline
                1                & 97.26                             & 0                                & 159.63                         & 100                               & 0                                & 174.23                         \\
                2                & 98.33                             & 0                                & 176.6                          & 89.73                             & 0                                & 186.43                         \\
                3                & 0.13                              & 43.33                            & 457.26                         & 7.66                              & 21.33                            & 410.53                         \\
                4                & 0                                 & 37.66                            & 547.5                          & 1.84                              & 21.66                            & 736.83                         \\
                5                & 71.32                             & 0                                & 379.13                         & 60.52                             & 0                                & 367.93                         \\
                6                & 96.32                             & 0                                & 165.06                         & 95                                & 0                                & 203.53                         \\
                7                & 99.74                             & 0                                & 162.06                         & 85.9                              & 0                                & 135.13                         \\
                8                & 34.3                              & 6                                & 520.93                         & 38.76                             & 2                                & 443.6                          \\
                \hline
                \textbf{Average} & 62.17                             & 10.87                            & 321.02                         & 59.92                             & 5.62                             & 332.27                         \\
            \end{tabular}
        \end{center}
    \end{table}

@@

    \begin{table}[htbp]
        \caption{PPO trained against all opponents (Gain)}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|c|}
                \hline
                \textbf{Opponent} & \multicolumn{5}{|c|}{\textbf{Difficulty}} \\
                \cline{2-6}
                & \textbf{\textit{1}} & \textbf{\textit{2}} & \textbf{\textit{3}} & \textbf{\textit{4}} & \textbf{\textit{5}} \\
                \hline
                1                      & 200.01              & 199.54              & 170.75              & 155.48              & 41.08               \\
                2                      & 200.01              & 200.01              & 182.81              & 168.81              & 168.51              \\
                3                      & 199.38              & 194.81              & 164.31              & 127.54              & 130.61              \\
                4                      & 186.14              & 180.61              & 154.23              & 181.58              & 60.28               \\
                5                      & 196.56              & 187.77              & 185.34              & 142.41              & 158.31              \\
                6                      & 196.35              & 174.43              & 179.19              & 23.84               & 9.88                \\
                7                      & 199.26              & 183.07              & 95.40               & 8.01                & 8.28                \\
                8                      & 196.57              & 169.31              & 123.00              & 41.34               & 10.01               \\
                \hline
                \textbf{harmonic mean} & 196.68              & 185.57              & 149.57              & 35.76               & 20.89               \\
                \hline
            \end{tabular}
            \label{PPO against all opponents gain}
        \end{center}
    \end{table}

    \begin{table}[htbp]
        \caption{PPO trained against all opponents (percent games lost)}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|c|}
                \hline
                \textbf{Opponent} & \multicolumn{5}{|c|}{\textbf{Difficulty}} \\
                \cline{2-6}
                & \textbf{\textit{1}} & \textbf{\textit{2}} & \textbf{\textit{3}} & \textbf{\textit{4}} & \textbf{\textit{5}} \\
                \hline
                1 & 0                   & 0                   & 20                  & 23.33               & 100                 \\
                2 & 0                   & 0                   & 0                   & 0                   & 0                   \\
                3 & 0                   & 0                   & 0                   & 13.33               & 3.33                \\
                4 & 0                   & 0                   & 0                   & 0                   & 60                  \\
                5 & 0                   & 0                   & 0                   & 0                   & 0                   \\
                6 & 0                   & 0                   & 0                   & 100                 & 100                 \\
                7 & 0                   & 0                   & 56.66               & 100                 & 100                 \\
                8 & 0                   & 0                   & 10                  & 100                 & 100                 \\
                \hline
            \end{tabular}
            \label{PPO against all opponents games lost}
        \end{center}
    \end{table}

    \subsubsection{A PPO agent for each opponent}
    In the second attempt to outscore the upper bound we have trained an agent
    for each of the $8$ opponents.
    Due to the high computational time this experiment was done only at
    difficulty 2 and the number of training epochs for PPO was decreased from 3000 to 1000.
    It won all its games against all opponents at difficulty 2.
    \begin{table}[htbp]
        \caption{PPO generalized vs PPO specialized vs NEAT specialized}
        \begin{center}
            \begin{tabular}{|c|c|c|c|}
                \hline
                \textbf{Opponent}      & \textbf{PPO g.} & \textbf{PPO s.} & \textbf{NEAT s.} \\
                \hline
                1                      & 199.54          & 199.67          & 190.01           \\
                2                      & 200.01          & 199.61          & 194.01           \\
                3                      & 194.81          & 199.94          & 180.01           \\
                4                      & 180.61          & 195.95          & 194.01           \\
                5                      & 187.77          & 198.03          & 194.01           \\
                6                      & 174.43          & 199.67          & 173.01           \\
                7                      & 183.07          & 197.73          & 177.01           \\
                8                      & 169.31          & 195.07          & 186.01           \\
                \hline
                \textbf{harmonic mean} & 185.57          & 198.19          & 185.67           \\
                \hline
            \end{tabular}
            \label{PPO generalized vs specialized vs NEAT}
        \end{center}
    \end{table}

    \subsection{Specialized PPO at difficulty 5}\label{subsec:specialized-ppo-at-difficulty-5}
    A PPO agent for each opponent.
    1000 training epochs per opponent.
    (10 million frames for each opponent).
    Harmonic mean of gains is 154.58.
    \begin{table}[htbp]
        \caption{Specialized PPO at difficulty 5}
        \begin{center}
            \begin{tabular}{|c|c|c|}
                \hline
                \textbf{Opponent} & \textbf{Gain} & \textbf{Percent games lost} \\
                \hline
                1                 & 166.01        & 13.33                       \\
                2                 & 197.18        & 0.00                        \\
                3                 & 72.28         & 100.00                      \\
                4                 & 191.23        & 0.00                        \\
                5                 & 196.71        & 0.00                        \\
                6                 & 198.76        & 0.00                        \\
                7                 & 176.01        & 0.00                        \\
                8                 & 172.61        & 0.00                        \\
                \hline
            \end{tabular}
            \label{PPO generalized at difficulty 5}
        \end{center}
    \end{table}

@@

    \subsection{Specialized PPO at multiple difficulties}\label{subsec:specialized-ppo-at-multiple-difficulties}

    \begin{table}[htbp]
        \caption{Specialized PPO against multiple difficulties (gain)}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|}
                \hline
                \textbf{Opponent} & \multicolumn{4}{|c|}{\textbf{Difficulty}} \\
                \cline{2-5}
                & \textbf{\textit{2}} & \textbf{\textit{3}} & \textbf{\textit{4}} & \textbf{\textit{5}} \\
                \hline
                1                      & 199.68              & 196.51              & 189.21              & 166.01              \\
                2                      & 199.61              & 199.91              & 199.21              & 197.18              \\
                3                      & 199.94              & 199.51              & 147.21              & 72.28               \\
                4                      & 195.95              & 196.14              & 198.81              & 191.23              \\
                5                      & 198.03              & 193.38              & 191.73              & 196.71              \\
                6                      & 199.67              & 195.18              & 196.85              & 198.76              \\
                7                      & 197.73              & 192.45              & 184.85              & 176.01              \\
                8                      & 195.07              & 185.37              & 178.05              & 172.61              \\
                \hline
                \textbf{harmonic mean} & 198.19              & 194.7               & 184.12              & 154.58              \\
                \hline
            \end{tabular}
            \label{Specialized PPO against multiple difficulties (gain)}
        \end{center}
    \end{table}

    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.5\textwidth]{images/specialized_ppo_harmonic_gain_per_diff.eps}
        \caption{Harmonic Gain of specialized PPO at multiple difficulties.}
        \label{fig:specialized_ppo_harmonic_gain_per_diff}
    \end{figure}

    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.5\textwidth]{images/specialized_ppo_gain_per_diff_per_opp.eps}
        \caption{Gain of specialized PPO at multiple difficulties for each opponent.}
        \label{fig:specialized_ppo_gain_per_diff_per_opp}
    \end{figure}

    \begin{table}[htbp]
        \caption{Specialized PPO against multiple difficulties (percentage games lost)}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|}
                \hline
                \textbf{Opponent} & \multicolumn{4}{|c|}{\textbf{Difficulty}} \\
                \cline{2-5}
                & \textbf{\textit{2}} & \textbf{\textit{3}} & \textbf{\textit{4}} & \textbf{\textit{5}} \\
                \hline
                1 & 0.00                & 0.00                & 0.00                & 13.33               \\
                2 & 0.00                & 0.00                & 0.00                & 0.00                \\
                3 & 0.00                & 0.00                & 36.67               & 100.00              \\
                4 & 0.00                & 0.00                & 0.00                & 0.00                \\
                5 & 0.00                & 0.00                & 0.00                & 0.00                \\
                6 & 0.00                & 0.00                & 0.00                & 0.00                \\
                7 & 0.00                & 0.00                & 0.00                & 0.00                \\
                8 & 0.00                & 0.00                & 0.00                & 0.00                \\
                \hline
            \end{tabular}
            \label{Specialized PPO against multiple difficulties (percentage games lost)}
        \end{center}
    \end{table}
